Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-08 main.tex
outline

\newcommand*{\LK}{\mathsf{LK}}
\newcommand*{\LKm}{\mathsf{LK + mix}}
\newcommand*{\MLL}{\mathsf{MLL}}
\newcommand*{\FOMLL}{\mathsf{MLL1}} 
\newcommand*{\FOMLLm}{\mathsf{MLL1 + mix}}
\newcommand*{\FOKS}{\mathsf{KS1}}

@@

@@

>>>>

\newcommand*{\LK}{\mathsf{LK}}
\newcommand*{\FOLK}{\mathsf{LK1}}
\newcommand*{\LKm}{\mathsf{LK + mix}}
\newcommand*{\MLL}{\mathsf{MLL}}
\newcommand*{\FOMLL}{\mathsf{MLL1^\times}} 
\newcommand*{\FOMLLm}{\mathsf{MLL1+mix}}
\newcommand*{\FOKS}{\mathsf{KS1}}
\newcommand*{\FOMLS}{\mathsf{MLS1^\times}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\set}[1]{\{#1\}}

@@

\section{Preliminaries: First-order Logic}\label{sec:fologic}

\subsection{Terms and Formulas}

\subsection{Sequent Calculus $\FOLK$}

\section{Preliminaries: First-order Graphs}\label{sec:fographs}

\subsection{Cographs}

\subsection{Fographs}

\section{First-order Combinatorial Proofs}\label{sec:focp}

\subsection{Fonets}

\subsection{Skew Bifibrations}

\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}

\section{Main Results}

\section{Translating between $\FOLK$ and $\FOKS$}

\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}

\subsection{Contraction and Weakining}

\subsection{A First Decomposition Theorem}

$$
\vlderivation{
  \vlde{\set{\wD,\cD}}{}{C}{
    \vlde{\FOMLS}{}{C'}{
      \vlhy{\ttt}}}}
$$

\section{Fonets and Linear Proofs}

\subsection{Unification Nets}

\subsection{Translation between Unification Nets and $\FOMLL$}

\subsection{Translation between Unification Nets and Fonets}

\section{Skew Bifibrations and Resource Management}

\subsection{From Contraction and Weakening to Skew Bifibrations}

\subsection{From Skew Bifibrations to Contraction and Weakening}

\section{Summary and Proofs of Main Results}

\bigskip
\hrule
\bigskip
